Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-27 src/tex/conclusion.tex
super basic conclusion....

Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
waves \citep{B_Farr_etal_2014,Littenberg_2015,MaMandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 
with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astro/physics that a better 
understanding of the black hole population will uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
sense of the data.

>>>>

Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 
with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astro/physics that a better 
understanding of the black hole population will uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
sense of the data.
